A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-07-07 src/paper.tex
WIP: Application Hosting Infrastructure

Since applications in the TV domain have the potential to reach out millions of users at the same time, it is interesting to consider the use of a cloud based platform for storing and processing data~\cite{Lee2010}.

>>>>

The application hosting infrastructure (AHI) consists of a server environment that provides the necessary computing resources to run a web application and make it available to client applications. This infrastructure can be owned by the CP or it can be hired from a third party service provider. As a matter of fact, the web applications hosted in the AHI are responsible for providing the interactive content that can be accessed by the second screen clients. In addition, the web applications offer features for storing and processing data.

Cloud computing can be used to quickly scale up and scale down according to workload demands. Since applications in the TV domain have the potential to reach out millions of users at the same time, it is interesting to consider the use of a cloud based platform for storing and processing data~\cite{Lee2010}.
